%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {Machine Learning Engineer (Graduate Internship) - Software Group} % Job title
    {European Southern Observatory (ESO)} % Organization
    {Paranal, Chile} %ce%% Location
    {Aug. 2023 - Jan. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered an API to streamline access to diverse data sources, including JIRA tickets and SVN logs, fostering enhanced accessibility and integration of user information across various platforms.}
        \item {Devised and implemented a reporting tool application using Streamlit Python's library, featuring customizable summarization levels tailored to user perspectives through utilizing Large Language Models (LLMs). Integrated JIRA tickets and associated commits into comprehensive reports spanning specified timeframes.}
	\item {Spearheaded prototyping initiatives utilizing vector databases focusing on OpenSearch and the Retrieval Augmented Generation (RAG) pattern. Contributed to developing projects showcasing applications such as similarity search, chatbots, and Q\&A apps.}
	\item {Delivered a presentation on LLMs and actively engaged in discussions on their strategic integration within the engineering department at Paranal Observatory.}
	\item {Developed an application utilizing the Google ORTools library to address the rostering problem for operational roles at the observatory.}
      \end{cvitems}
    }

  \cventrytwopositions
    {Payops and RiskFraud Lead}
    {Compraquí - BancoEstado subsidiary}
    {Santiago, Chile}
    {Oct. 2019 - Oct. 2020}
    {
      \begin{cvitems}
	      \item {Led the Payops and RiskFraud team in processing payments for over 50k merchants nationwide, focusing on minimizing fraud and preventing service misuse in the card payment network.}
	      \item {Developed various data products, including reports and dashboards, utilizing code to automate data extraction, preprocessing, and presentation.}
	      \item {Implemented the risk and fraud process, creating features based on transaction details like transaction amount, deviation from average tickets by merchant category, and transaction frequency. Developed an outlier detection model to calculate a transaction score.}
      \end{cvitems}
    }
    {Manager Payops and Analytics}
    {Oct. 2020 - May. 2021}
    {
      \begin{cvitems}
        \item {Oversight of the complete payment process for merchants, leading a team of four analysts to ensure a seamless end-to-end payment workflow.}
        \item {Guided the analytics teams to provide data and insights to various company departments and the management team, facilitating informed decision-making for the business.}
        \item {Coordinated the relationship with the acquirer, defining services and needs for information required by the payment and data processes.}
	\item {Designed, developed and documented the critical processes within the Payops and Analytics area.}
	\item {Organized and documented incidents in a centralized repository, efficiently managing their resolution with the technological provider.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Economic Financial Analyst - Macroeconomic Statistic Division} % Job title
    {Central Bank of Chile} % Organization
    {Santiago, Chile} %ce%% Location
    {Oct. 2016 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for deploying and maintaining the statistical data process to elaborate the local fixed-income quarterly publications. Includes processing multiple data sources and translating from granular data to macro-financial concepts consistently with other macroeconomic statistics.}
        \item {Write technical reports and make periodic presentations to the stakeholders about the economic and financial scenario of local fixed-income markets.}
        \item {Implement and publish the Handbook of Securities Statistics for Chile, one of the nine Special Data Dissemination Standards (SDDS plus) items, the most advanced standard for economic-financial statistics dissemination worldwide. At that time, Chile was one of the two countries in LATAM to meet these standards and have comparable statistics with other countries. More information \href{https://www.bcentral.cl/en/detail-news-and-publications/-/asset_publisher/Exzd7l9NC3Y6/content/id/2228947}{here}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
