%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching Experience - Extracurricular}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {MDS7203: Deep Generative Models (Teaching Assistant)} % Affiliation/role
    {Universidad de Chile}
    {Santiago, Chile}
    {Aug. 2023 - Dec. 2023}
    {
      \begin{cvitems}
        \item {Contributed to designing and leading a master's level data science course, emphasizing theoretical fundamentals and algorithms for building and training generative models. Covered key topics like Variational Autoencoders, Score-based models, Diffusion models, and Autoregressive models. Actively participated in crafting curriculum materials and hands-on activities for a dynamic learning experience.}
      \end{cvitems}
    }
  \cventry
    {Speaker} % Affiliation/role
    {Data Visualization Talk, Women in Data - Guatemala Chapter (NPO)} % Organization/group
    {Remote} % Location
    {Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A talk focused on the skills for moving from a beginner to an intermediate user in data visualization. The topics included composing data visualisations by layers, knowing some of the best practices, and customising many visual features to maximise communication using python.}
        \item {Slide, video recording, and code for my talk: \url{https://github.com/alcazar90/WomenInData-Guatemala2021}}
      \end{cvitems}
    }
    
  \cventry
    {Speaker} % Affiliation/role
    {Data Visualization Workshop, Ministry of Social Development and Family} % Organization/group
    {Santiago, Chile} % Location
    {Aug. 2019 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A five-session Data Visualization workshop focused on both hands-on and theoretical material addressed for professionals in the public sector.
}
      \end{cvitems}
    }
   
  \cventrytwopositions
    {ECP7-1: Data Analysis with R Programming (Part-time Professor)}
    {Universidad de Chile}
    {Santiago, Chile}
    {Sep. 2018 - Dec. 2018}
    {
      \begin{cvitems}
        \item {This was the first course imparted at the Institute of Communication and Image (ICEI) that gives data science tools for data wrangling and visualization for applying to data journalism projects.}      
      \end{cvitems}
    }
    {EI3001-2: Data Journalism with Python (Part-time Professor)}
    {Mar. 2019 - Aug. 2019}
    {
      \begin{cvitems}
        \item {An interdisciplinary course dictated for engineering and journalism students; focused on providing data science tools to apply to data journalism projects.}
      \end{cvitems}
    }


%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
